\Large Generative Dynamics of Supreme Court Citations

### 2020-04-09 Tex/paper.tex
Wrote about Transitivity terms in section 4.1.2 Dependence Terms

We include a dependence term to account for each of the dynamics that we hypothesize will characterize the Supreme Court Citation Network---transitivity, reciprocity, popularity, and activity. We expect that the coefficients associated with each of these dependence effects will be positive.

The common dependence effects for these four dynamics are the number of triangles (case $i$ cites cases $j$ and $k$, and case $j$ cites case $k$), the numnber of mutual dyads (case $i$ cites $j$ and vice versa), the numnber of out-2-stars (case $i$ cites $j$ and $k$), and the number of in-2-stars (case $i$ is being cited by cases $j$ and $k$) in $C_{\leq t}$. Unfortunately, adding the triangle, out-2-star, or in-2-star statistic causes model degeneracy \citep{Handcock.2003}. Model degeneracy occurs when the model places most of its probability mass on just a few networks, usually the empty and the full network. In this scenario, the simulated networks are too different from the observed network, making the underlying distribution defined by the model extremly unrealistc.

@@

% Transitivity

>>>>

We include dependence terms to account for each of the dynamics that we hypothesize will characterize the Supreme Court Citation Network---transitivity, reciprocity, popularity, and activity. %We expect that the coefficients associated with each of these dependence effects will be positive.

The common dependence effects for these four dynamics are the number of triangles (case $i$ cites cases $j$ and $k$, and case $j$ cites case $k$), the numnber of mutual dyads (case $i$ cites $j$ and vice versa), the numnber of out-2-stars (case $i$ cites $j$ and $k$), and the number of in-2-stars (case $i$ is being cited by cases $j$ and $k$) in $C_{\leq t}$. Unfortunately, adding the triangle, out-2-star, or in-2-star statistic causes model degeneracy \citep{Handcock.2003}. Model degeneracy is a common obstacle when fitting ERGMs and occurs when the model places most of its probability mass on just a few networks, usually the empty and the full network. In this scenario, the simulated networks are too different from the observed network, making the underlying distribution defined by the model extremly unrealistc.

@@

% Transitivity
We include two statistics to account for different types of transitivity.
The first transitivity statistic calculates the number of transitive ties, $i \to j$, where there is a directed path of length two from $i$ to $j$ through at least one case $k$, and $j$ and $k$ were written during a different term than $i$. We will refer to this statistic as the \textit{different term transitivity} statistic. As illustrated in chapter 2 we theorize Supreme Court citations to pattern a high degree of transitivity. As a result, we expect positive parameter estimates for the different term statistics.

The second transitivity statistic is the \textit{geometrically weighted edgewise shared partners} (gwesp) statistic introduced by \citet{hunter2006inference}. For directed networks the edgewise shared $r$-partners statistic ($ESP_r$) can take multiple forms, but we integrate the definition where cases $i$ and $j$ that are connected by a citation, also cite $r$ common other cases. Similar to the gwidegree-statistic the gwesp-statistic incorporates a network's edgewise shared partners distribution by replacing $D_r$ by $ESP_r$.
Note that unlike the different term transitivity statistic the gwesp statistic does not require the cited cases to be written in a previous term.

 \textit{GOF-plot?}\\
